---
title: "HW4"
author: "Xueying Zhou, Zimin Zhuang"
date: "3/19/2018"
output:
  pdf_document: default
  html_document: default
---
#Problem 1
##(a)
Recall the Ito's formula
$$dV = \frac{\partial V}{\partial t} dV + \frac{\partial V}{\partial r} dr 
      + \frac{1}{2} \frac{\partial^2 V}{\partial r^2} dr^2$$
Let $V = e^{\alpha t} (r(t) - b)$, then we have
\begin{align*}
\frac{\partial V}{\partial t} &= \alpha e^{\alpha t} (r(t) - b)\\ \\
\frac{\partial V}{\partial r} &= e^{\alpha t}\\ \\ 
\frac{\partial^2 V}{\partial r^2} &= 0\\ \\
\end{align*}
Substitute into the Ito Formula, we have
\begin{align*}
dV &= \alpha e^{\alpha t} (r(t) - b) dt + e^{\alpha t} dr\\ \\
dV &= \sigma dW(t)
\end{align*}
Integrate both sides from $t$ to $t + \Delta$,
\begin{align*}
e^{\alpha (t + \Delta)} [r(t+ \Delta) - b]
&= e^{\alpha t} (r(t) - b) + \sigma [ W(\Delta + t) - W(t)]\\ \\ 
r(t+ \Delta) - b
&= e^{- \alpha t} (r(t) - b) + e^{- \alpha (t+ \Delta)} \sigma [ W(\Delta + t) - W(t)]\\ \\
r(t+ \Delta) &= e^{- \alpha \Delta} r(t) + b(1 - e^{- \alpha \Delta})
                + \frac{\sigma}{\sqrt{2 \alpha}} \sqrt{1 - e^{-2 \alpha \Delta}} Z
\end{align*}
Where $Z \sim N(0, 1)$.

##(b)
First, we store the values of $\alpha, b,\sigma$ into a $3*18$ matrix for further usage. Each column present one possible combination of the three input parameters.\
Then we define the function 'OUprocess', as obtained in part $(a)$, to be called iteratively to calculate the values of $r(t)$ within the given time interval $[0,T]$ for a specified combination of all the input parameters.\
Finally, a loop is built to call the function for $18$ times for all the $18$ combinations, and the results are plotted with corresponding titles clarifying the $\alpha, b,\sigma$ combinations.
```{r}
#Input Parameters
param.alpha <- c(rep(0.1, 6), rep(1, 6), rep(5, 6))
param.b <- rep(c(-5, -5, -5, 5, 5, 5), 3)
param.sigma <- rep(c(0.1, 0.2, 0.5), 6)
#Rowbind parameters
param <- rbind(param.alpha,param.b, param.sigma)
#Define a OU process
OUprocess <- function(alpha, b, sigma, r.ini, T.t, Delta){
  #Initialize
  r <- c()
  t <- 1
  r[1] <- r.ini
  #Iterations
  for (t in 1:(T.t/Delta)){
    z <- rnorm(1)
    r[t + 1] <- exp(-alpha * Delta) * r[t] + b*(1 -  exp(-alpha * Delta)) +
      (sigma / sqrt(2*alpha)) * sqrt(1 - exp(-2 * alpha * Delta)) * z 
    t <- t + 1
  }
  return(r)
}

#Presenting all 18 combinations
i <- 1
for (i in 1:18){
  #T.t <- 500
  #Delta <- 1/500
  #r.ini <- 1
  result <- OUprocess (param[1, i], param[2, i], param[3, i], 1, 500, 1/500)
  plot(result, type = "l", xlab = "Interations", ylab = "r(t)",
       main = paste0("OU process of ", param[1, i], ", ", param[2, i], ", ", param[3, i], "."))
}
```
As shown in the graphs, the value of $\alpha$ presents the speed for $r(t)$ to hit $b$; the value of $\sigma$ presents the volatility.

#Problem 2
First, we define a function for the Brownian Motion according to its properties that $W(0)=0$ and $W(t) \sim N(0, \sqrt{t})$.\
Then we calculate the difference by spliting $[0,T]$ into n sub-intervals for the lefthand part and summing up the discrete values to approximate the integral as required. \
Third, we define the function to be called to obtain the MC estimate of $\sqrt{E[D^2]}$ for a deterministic n with the required $10,000$ observations, and apply it with $n = 10, 100, 1000$ to get the corrosponding results.
```{r}
#Define a BM
i <- 1
W <- c()
T.t <- 1
BM <- function(n, T.t){
  W[1] <- 0
  ending <- n + 1
  for(i in 2:ending){
    increment <- rnorm(1, 0, sqrt(T.t/n))
    W[i] <- W[i-1] + increment
  }
  return(W)
}

#Define the calculation of difference D
D <- function(n, T.t){
  w <- BM(n, T.t)
  ito <- 1 - exp(T.t/2) * cos(w[n+1])
  approx <- 0
  for(i in 1:n){
    approx.update <- exp((i-1)*T.t/(2*n)) * sin(w[i]) * (w[i+1]-w[i])
    approx <- approx + approx.update
  }
  d <- approx - ito
  return(d)
}

#Defind the MC estimation of sqrt(E(D)^2)
ED <- function(n,T.t){
  ed <- rep(0, 10000)
  i <- 1
  for (i in 1:10000){
    ed[i] <- (D(n, T.t))^2
  }
  return(sqrt(mean(ed)))
}


#Results for n = 10, 100 and 1000
ED(10, 1)

ED(100, 1)

ED(1000, 1)

```

#Problem 3
##(a)
To apply the Ito's formula, we let $V = log S(t)$, then we have
\begin{align*}
\frac{\partial V}{\partial t} &= 0 \\ \\
\frac{\partial V}{\partial r} &= \frac{1}{S(t)}\\ \\
\frac{\partial^2 V}{\partial r^2} &= -\frac{1}{S^2(t)}
\end{align*}
Therefore,
$$dV = \frac{1}{S(t)} dS -\frac{1}{S^2(t)} dS^2$$
with $dS^2 = \sigma^2 S^2(t)dt$
$$dV = (r - \frac{\sigma^2}{2}) dt + \sigma dW$$
Integrate both sides from 0 to t, noticing that $S(0) = 1$,
$$S(t) = e^{(r - \frac{\sigma^2}{2})t + \sigma \sqrt{t}Z}$$
let $X = (r - \frac{\sigma^2}{2})t + \sigma \sqrt{t}Z$
\begin{align*}
E[X]      &= (r - \frac{\sigma^2}{2})t\\ \\
Var(x)    &= \sigma^2 t\\ \\
E[S(t)]   &= e^{E[X] + \frac{1}{2} Var(x)}\\ \\
E[S(t)]   &= e^{rt}\\ \\
E[S(t_i)]  &= e^{rt_i}\\ \\
K = E[S_A] &= E[\frac{1}{k} \sum^k_{i = 1} S(t_i)]\\ \\
           &=\frac{1}{k}E[\sum^k_{i = 1} S(t_i)]\\ \\
           &=\frac{1}{k} \sum^k_{i = 1} e^{rt_i}]\\ \\
\end{align*}

##(b)
First we define the function 'GeoBM' with input parameters $r, \sigma, t$ for the Geometric Brownian Motion to obtain values of $S(t)$ within time interval $[0,t]$, knowing it has the solution 
$S(t_i) = S(t_{i - 1})e^{(r - \frac{\sigma^2}{2})(t_i-t_{i-1})+\sigma \sqrt{t_i-t_{i-1}}Z}$ \
Then, we define the function for the Asian Option 'SA' with input parameters $r, \sigma, t$, which is the average of the the stock prices calculated in the first part.
Then, the function 'K' for $e^{-rT}(S_A - K)_+$ is defined with inputs parameters $r, \sigma, t$. Further, in the function to estimate the price, we build a loop to call 'K' for $10^5$ times as asked, with given parametes $r = 0.11, \sigma = \sqrt{0.3}, (t_1, t_2, t_3, t_4)= (1, 5, 10, 20)$ and obtain their mean to finish the estimation.
```{r}
#Define a geometric Brownian motion
S <- c()
GeoBM <- function(r, sigma, t){
  S[1] <- 1
  for(i in 2:length(t)){
    diff.t <- t[i] - t[i-1]
    z  <- rnorm(1, 0, sigma * sqrt(diff.t))
    log.increment <- r * (diff.t)  - 0.5 * ((sigma)^2) * (diff.t) + z
    S[i] <- exp(log(S[i - 1]) + log.increment)
  }
  return(S)
}


#Define the calculation of SA
SA <- function(r, sigma, t){
  s <- GeoBM(r,sigma,t)
  SA <- (sum(s[2:length(t)])) / (length(t) - 1)
  return(SA)
}

K <- function(r,sigma,t){
  value <- max((SA(r,sigma,t) - sum((exp(r * t[2:length(t)])) / (length(t) - 1))), 0)
  k <- (exp(-1 *r * t[length(t)])) * value
  return(k)
}

#Define the calculation of Price
P <- function(r, sigma, t, replica){
  P <- rep(0, replica)
  for (i in 1:replica){
  P[i] <- K(r, sigma, t)
  }
  return(mean(P))
}

#Report Estimation
P(0.11, sqrt(0.3), c(0, 1, 5, 10, 20), 100000)
```

